testfigs

### 2016-06-28 inst/documents/testfigs.Rmd
for testing fig positioning

---
title: "paper2_resistance_mechanisms_mixtures"
output: pdf_document
#output: word_document
author: "Andy South, Ian Hastings and Bethany Levick"
date: "`r Sys.Date()`"
---

```{r,echo=FALSE,results='hide'}
  library(resistance)
  library(ggplot2)
```

### version 3

# Mechanisms by which insecticide resistance can be influenced by strategies of insectcide use : a simple theoretical exploration.

(This file is automagically generated by R from paper2_resistance_mechanisms_mixtures.Rmd)
Target : Malaria journal

#### TO DO
1. decide whether to use selective advantage or rr restoration coefficient

## Abstract

This paper explores the mechanisms by which insectide resistance is expected to increase with the use of insecticides in isolation, sequence/rotation and mixtures. It is aimed at a readership with limited experience of population genetics and resistance. It uses a model representing two independent loci coding for resistance to two insecticides. It explores factors that are expected to influence the development of resitance, notably the starting frequency of resistance alleles, their dominance, the exposure of insects to the insecticides, the effectiveness of the insecticides, the selective advantage of resistance and the dominance of the alleles. There is uncertainty about the values of these parameters in field situations. We demonstrate how the values of these parameters are expected to influence the development of resistance and the relative benefits of alternative insecticide application strategies. We describe an R package and user-interface that allows further exploration of the development of resistance. The user-interface (https://andysouth.shinyapps.io/MixSeqResist1) allows replication of our results and exploration of what happens when inputs are changed outside of the ranges we have used.

## Introduction

Insecticide resistance is a problem for malaria (GPIRM), other vector borne diseases and agriculture.

Insecticide resistance becomes a problem when genes coding for resistance firstly arise in a population and secondly increase in frequency. We concern ourselves with this second process of how insecticide resistance increases in frequency within a population.

The changing frequency of insecticide resistance is a population genetic process that can be influenced by :

Parameter  | Description
------------------- | -------------------------------------------------------
1. Effectiveness | proportion of exposed insects with the susceptible allele that are killed by the insecticide
2. Exposure | proportion of the insect population that are exposed to the insecticide
3. Dominance | dominance of the resistance allele relative to the susceptible allele
4. Selection Coefficient  | selective advatange of resistance in the presence of the insecticide
5. Frequency  | frequency of resistance alleles within the population

We use a 2-locus population genetic model of insecticide resistance (Hastings et al. in press) to illustrate the mechanisms by which these parameters are expected to influence the development of insectide resistance under alternative insecticide use strategies. Hastings et al. (in press) describe the technical details of the model and explore large parameter ranges. In contrast we provide an accessible summary of the model and use selected parameter values to demonstrate mechanisms that can influence the development of resistance.

## Methods

*accessible summary of the model*

## Results

For single insecticide use, increasing the values of either effectiveness, exposure, dominance, or the selective advantage of RR, all lead to faster resistance (Figs a1-4). (In these four plots the value of the inputs not being varied are set at a constant 0.5).

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.2,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.8,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  listOut <- runModel2( input )

  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=phi.SS1_A0)) + 
         labs(colour = "effectiveness") +
         coord_trans(y = "log10") +    
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a1. Effectiveness effect on single insecticide.")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  exposure <- 0.2
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  exposure <- 0.5
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  exposure <- 0.8
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  listOut <- runModel2( input )

  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=exposure)) + 
         theme_bw() +
         labs(colour = "exposure") +
         coord_trans(y = "log10") +    
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a2. Exposure effect on single insecticide.")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  #this sets exposures according to whether insecticide1, 2 or mixture
  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.2, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.8, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  listOut <- runModel2( input )

  #plotallele.freq.andy(listOut, locus="1", sex="mf_mean", add_legend=FALSE)

  # now doing a better way
  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=h.RS1_A0)) + 
         theme_bw() +
         labs(colour = "dominance") +
         coord_trans(y = "log10") + 
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a3. Dominance effect on single insecticide.")

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.2,
                      rr_restoration_ins2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.8,
                      rr_restoration_ins2 = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  listOut <- runModel2( input )

  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=rr_restoration_ins1)) + 
         theme_bw() +
         labs(colour = "selective advantage") +
         coord_trans(y = "log10") +   
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a4. Selective advantage of RR effect on single insecticide.")

When two insecticides are used the relative performance of a mixture strategy compared to sequential use is determined by the values of these four inputs.

With all control inputs set equal at 0.5 resistance arises slower for sequential than mixture (Fig. 1 A). Resistance to both insecticides in the mixture follow the same path and reach the threshold at the same time. When used in sequence the curve for each insecticide individually is steeper but, because they happen one after the other, it takes longer to reach the resistance threshold for both.

**Effectiveness of the insecticides**
A more effective insecticide prompts increased time-to-resistance when used in a mixture. This contrasts with the earlier result showing that when used in isolation a single insecticide prompts a shorter time-to-resistance.

@@

In a mixture the mechanism is that a more effective insecticide provides greater protection to the other. For example taking the previous scenario and increasing the effectiveness of one insecticide from 0.5 to 0.9 increases the time-to-resistance for the 2nd insecticide from around 45 to 75 generations (Fig. 1 B). In the plot you can see that resistance to insecticide1 (with the increased effectiveness) rises at a similar speed to Fig. 1A. In contrast resistance to insecticide2 increases more slowly initially. Once insecticide1 reaches it's resistance threshold (around 40 generations), the curve for insecticide2 becomes steeper. This can be explained by the mechanism that once insecticide1 has become ineffective due to resistance it stops killing indivduals that are resistant to insecticide2 and thus stops 'protecting' it from it's own rise in resistance.

When the effectiveness of both insecticides are increased to 0.9 the time-to-resistance is increased still further to around 125 generations (Fig. 2). In this case the curves for the rise in resistance to each insecticide are identical. The curves are shallower than previous plots because individuals that are resistant to each insecticide are being killed by the other thus reducing the increase in resistance alleles. As the resistance frequencies go above 10% around generation 100 both insecticides provide less protection to the other and the slope of the resistance curve increases.

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="Effectiveness of both insecticides 0.9"}

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.9 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )

**Dominance of resistance alleles**
Increasing the dominance of the alleles within a mixture has the same direction of effect as it does for sole use. Increasing the dominance of the allele corresponding to insecticide1 from 0.5 to 0.9 decreases the time-to-resistance to insecticide1 from 40 to 30 generations but leaves the time-to-resistance for the mixture the same (Fig. 3A). Setting the dominance for both alleles to 0.9 reduces the time-to-resistance for the mixture to 30 generations (Fig. 3B). In both of these cases sequential use continues to have a longer time-to-resistance.

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Dominance of insecticide1 0.9, B. Dominance of both insecticides 0.9"}

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.' )
#cat("Dominance of insecticide1 0.9")

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.9 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab='', main='B.' )
#cat("Dominance of both insecticides 0.9")

**Selective advantage of resistance**
#TODO replace Figs 6,7,8 with AA,BB,CC below and modify this text
Decreasing the selective advantage of resistance to insecticide1 from 0.5 to 0.1 increases it's time-to-resistance in the mixture from 40 generations to 150, and has a similar effect on it's use in isolation (Fig. 6). However, it has little effect on resistance to insecticide2. Because of this sequential use continues to generate a longer time-to-resistance than the mixture. Decreasing the selective advantage of both alleles to 0.1 results in a longer time-to-resistance of 200 generations for the mixture (Fig. 7), however the relative shape of the resistance curves remains the same as in Fig. 1, with sequential use continuing to generate longer time-to-resistance.

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 6. Selective advantage of insecticide1 0.1")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 7. Selective advantage of both insecticides 0.1")
```

Taking this scenario of lower selective advantage and increasing the effectiveness of both insectides from 0.5 to 0.7 shows again how the change in effectiveness has a greater effect on the mixture than sequential making the mixture preferable (compare Fig. 8 to Fig. 7).

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 8. Selective advantage of both insecticides 0.1, effectiveness to 0.7")
```

#cool contrast between these scenarios modifying effectiveness and rr_restoration in which all defaults set to 0.5 except
TODO incorporate this into text above

#AA effectiveness I1 to 0.8 causes mixture to be slower, although I1 is faster it protects I2 in mixture, making mixture slower
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. AA. effectiveness to 0.8")
```

#BB rr advantage I1 to 0.8 sequential remains slower, although I1 is faster as in previous it provides less protection to I2 in the mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. BB rr_restoration I1 0.8")
```

#CC rr advantage I2 to 0.2 sequential remains slower (just), I2 slower than I1 in mixture similar to AA but receives less protection in mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.2 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. CC. rr_restoration I2 0.2")
```

**Exposure**
Increasing exposure to 0.9 reduces time-to-resistance for both mixture and sequential scenarios (Fig. 9). The change in exposure has a greater effect on the mixture relative to the sequential strategy and this results in a greater relative benefit for sequence versus mixture. Setting the effectiveness of both insecicides to 0.7 (while keeping all other inputs at 0.5) results in mixture being slightly favoured (Fig. 10), then making the increase in exposure from 0.5 to 0.9 results in a switch to sequential being the favoured strategy (Fig. 11). This demonstrates how higher exposures can favour sequential use.

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 9. Exposure 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 10. Effectiveness 0.7, sequence favoured")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 11. Effectiveness 0.7, Exposure 0.9, mixture favoured")
```

## Discussion

**single insecticide**

Parameter to increase  | effect on resistance | Mechanism
------------------ | ------- | ---------------------------------------------------
1. Effectiveness | faster | increased deaths of susceptibles
2. Exposure | faster | increased deaths of susceptibles
3. Dominance | faster | increased survival of heterozygotes
4. Selective advantage | faster | increased survival of resistants
5. Frequency  | faster | less change needed to reach resistance threshold

**mixture**

Parameter to increase  | effect on resistance | Mechanism
------------------ | ------- | ---------------------------------------------------
1. Effectiveness | **slower** | increased deaths of individuals resistant to the other insecticide
2. Exposure | faster (but not as fast as for single) | increased deaths of individuals resistant to the other insecticide
3. Dominance | faster | increased survival of resistants
4. Selective advantage | ?faster | increased survival of resistants
5. Frequency  | faster | less change needed to reach resistance threshold

**difference between mixture and sequential use**

Parameter to increase  | relative performance mix versus seq | Mechanism
------------------ | ------- | ---------------------------------------------------
1. Effectiveness | mixture | faster resistance for single use and slower resistance in mixture
2. Exposure | sequence | faster resistance for mixture and sequence but has a greater effect on mixture
3. Dominance | ? | ?
4. Selective advantage | ? | ?
5. Frequency  | ? | ?

(@) In a mixture each insecticide reduces the rate of increase in resistance to the other by killing individuals that are resistant to the other.

(@) In a mixture the effectiveness of one insecticide has major effects on the resistance of the other. In contrast the dominance and selective advantage of one insecticide has less effect on the resistance of the other. For exposure we have kept values the same for each insecticide the same (to represent a mixture in which the 2 insecticides are applied together). However we predict that if they were applied separately then (similar to effectiveness) the level of exposure to one insecticide would influence the time-to-resistance of the other.

(@) In a mixture higher effectiveness of either insecticide kills more individuals resistant to the other and thus increases time-to-resistance for the other. Thus although increasing effectiveness of an insecticide decreases time-to-resistance when used alone, when used in a mixture time-to-resistance for both insecticides is increased.

(@) For a mixture of 2 insecticides with differing effectiveness. Resistance to the insecticide with a greater effectiveness increases faster. The less effective insecticide is 'protected' by the more effective. Resistance to the less effective insecticide increases slowly until resistance to the more effective insecticide reaches a high level at which point it starts to increase faster.

(@) Increasing exposure gives shorter time-to-resistance for both mixtures and sequences due to increased deaths of susceptibles creating a higher selection pressure. In a mixture the effect of exposure is greater and this means that increasing exposure can make sequences preferable to mixtures. The reason for the greater effect of exposure on mixtures could be that exposure is having both a direct effect on each insecticide and an indirect effect on the other. Thus higher exposures lead to faster resistance in each insecticide (direct), in turn increased resistance to each insecticide reduces the 'protection' that it gives the other, leading to faster resistance in the other (indirect). This could act as a postive feedback loop where faster resistance in one contributes to faster resistance in the other.

## References
1. GPIRM
1. Curtis 
1. Mani GS. Evolution of resistance in the presence of two insecticides. Genetics 1985;109(4):761–83.
1. Birget 2015

## Todo

1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? Is it because the exposure to one insecticide also effects the development of resistance in the other ?
1. create some code to enable plotting 2 scenarios side-by-side
1. re-read GPIRM
1. can I develop explanatory diagrams to describe the input parameters ?
1. mention generation time of 1 month
1. look at effect of sex linkage

>>>>

---
title: "testfigs"
output: pdf_document
#output: word_document
author: "Andy South"
date: "`r Sys.Date()`"
---

#testing getting figures side-by-side

```{r,echo=FALSE,results='hide'}
  library(resistance)
  #library(ggplot2)
```

why are the figs being pushed down the page ....

@@
